### 2014-03-16 src/discussion.Rnw
Fix mistake
Shortening table description a little bit
Fix up discussion

section{Discussion}
\label{sec:discussion}

@@

% About Randoop and Original
Analyzing the scores further, we note that the accuracy of prediction
($R^2$) achieved by sampling is generally lower for generated test
suites. As the sampling denominator increases, the correlation
reduces drastically for generated test suites while correlation remains strong
for original test suites
Secondly, we also observe that the multiplier factor $\beta_1$ 
is smaller for generated test suites than original test suites. This
observation holds good for all sampling and operator selection strategies
examined.  Both these factors together suggest that generated
test suites have a higher variability in their sampled mutation scores than
original test suites. We note that since $\beta_1$ was generally smaller
for generated test suites than original test suites, the full mutation score
corresponding to a sampled mutation score for generated test suites would
be lower than what would be expected from the original test suite.
Secondly, the amount of reduction that can be gained by sampling that must reach a given correlation is lower for generated test suites.

% Different sampling strategies
Considering different sampling strategies, based on their stability and mutation
reduction achieved, we note that using simple sampling (\textit{sample(x)})
produced the most stable results. For both generated and original test suites,
this strategy produced valid results for all different scopes and sampling
ratios. It also was able to achieve the highest mutation reduction of $72.63$,
that is only $1.37\%$ of the original mutants were needed to produce a highly
correlated ($R^2 = 0.97$) mutation score, with minimal deviation
($\sigma = 6.36$) for original test suites. While the correlation is weaker for
generated test suites it is still quite strong, with $R^2 = 0.90$

Our \textit{round(x)}, the strategy of ignoring low complexity elements,
did not pay off, with line scope having a tendency to become unstable and
inaccurate at low sampling ratios. At very low sampling ratio ($1/64$), the
strategy with method scope also becomes unstable and inaccurate. On the whole
\textit{round(x)} did not perform as well as \textit{sample(x)}

The strategy of \textit{ceil(x)} also did not perform well. While the
results were generally stable, the reduction ratios achieved were lower than
\textit{sample(x)}, with similar correlations.

@@

Considering different sampling strategies, we see a few general patterns. The
first is that sampling strategy can predict the final score with very
minimal loss up to a fraction of $\frac{1}{64}$ of the total
number of mutants (our experiments suggest up to $70$ times reduction,
with a low standard deviation of $6.72$). We did not cut off with the 99\%
rule as mentioned by Zhang et al.~\cite{zhang2013ase} (originally proposed
by Offutt et al.~\cite{offutt1996experimental} for a different measurement),
and instead chose to observe that we obtained $R^2 > 0.96$ which provides
a high confidence in the accuracy of prediction.

>>>>

\section{Discussion}
\label{sec:discussion}

@@

% About Randoop and Original
Analyzing the scores further, we note that the correlation
($R^2$) achieved by sampling is generally lower for generated test
suites. As the sampling denominator increases, the correlation
reduces drastically for generated test suites while correlation remains strong
for original test suites.
Secondly, we also observe that the multiplier factor $\beta_1$
is smaller for generated test suites than original test suites. This
observation holds good for all sampling and operator selection strategies
examined.  Both these factors together suggest that generated
test suites have a higher variability in their sampled mutation scores than
original test suites. We note that since $\beta_1$ was generally smaller
for generated test suites than original test suites, the full mutation score
corresponding to a sampled mutation score for generated test suites would
be lower than what would be expected from the original test suite.
Further, the amount of mutant reduction possible such that the sampled
mutation scores still has a high enough correlation with the total score
is lower for generated test suites.

% Different sampling strategies
Considering different sampling strategies, based on their stability and mutation
reduction achieved, we note that using simple sampling (\textit{sample(x)})
produced the most stable results. For both generated and original test suites,
this strategy produced valid results for all different scopes and sampling
ratios. It also was able to achieve a highest mutation reduction of $72.63$,
with high stability. That is, only $1.37\%$ of the original mutants were needed
to produce a highly correlated ($R^2 = 0.97$) mutation score, with minimal deviation
($\sigma = 6.36$) for original test suites. While the correlation is weaker for
generated test suites it is still quite strong, with $R^2 = 0.90$

Our \textit{round(x)}, the strategy of ignoring low complexity elements,
did not pay off, with line scope having a tendency to become unstable and
low correlated at low sampling ratios. At very low sampling ratio ($1/64$), the
strategy with method scope also becomes unstable and low correlated. On the whole
\textit{round(x)} did not perform as well as \textit{sample(x)}

The strategy of ensuring coverage with \textit{ceil(x)} also did not perform
well. While the results were generally stable, the reduction ratios achieved
were lower than \textit{sample(x)}, with similar correlations.

@@

Considering different sampling strategies, we see a few general patterns. The
first is that sampling strategy can predict the final score with very
minimal loss up to a fraction of $\frac{1}{64}$ of the total
number of mutants. We did not cut off with the 99\% rule as mentioned
byZhang et al.~\cite{zhang2013ase} (originally proposed
by Offutt et al.~\cite{offutt1996experimental} for a different measurement),
and instead observe that we obtained $R^2 = 0.97$ which provides
a high confidence in the accuracy of prediction of the full score.
